On exponential sums arising from the classical doubling method

### 2025-03-21 paper.tex
Changes with Calvin

	\item (Special even orthogonal groups): $\quadraticExtension = \finiteField$ and $\epsilon_{\hermitianSpace} = 1$. Denote $\dim_{\finiteField} \hermitianSpace = 2n$. It follows by definition that every element $g \in \IsometryGroup\left(\hermitianSpace\right)$ satisfies $\left(\det g\right)^2 = 1$. Similarly, every element $g \in \widetilde{\IsometryGroup\left(\hermitianSpace\right)}$ satisfies $\left(\det g\right)^2 = \similitudeCharacter\left(g\right)^{2n}$. In this case, we obtain the connected components of the identity by adding a restriction on the determinant: We have that $G$ consists of all elements $g \in \IsometryGroup\left(\hermitianSpace\right)$ with $\det \hermitianSpace = 1$, and that $\GroupExtension{G}$ consists of all elements $g \in \GroupExtension{\IsometryGroup\left(\hermitianSpace\right)}$ such that $\det g = \similitudeCharacter\left(g\right)^n$. There are two cases here.

@@

\begin{example}
	Take $\algebraicGroup{T}'_2 = \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme}$ and $$\algebraicGroup{T}_2 = \left\{x \in \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme} \mid x \involution{x} = 1 \right\}.$$
	Then $\left(\algebraicGroup{T}'_2\right)^{\Frobenius} = \multiplicativegroup{\finiteFieldExtension{2}}$ and $\algebraicGroup{T}_2^{\Frobenius} = \NormOneGroup{2}$. Let $\theta \colon \NormOneGroup{2} \to \multiplicativegroup{\ladicnumbers}$ be a character, and let $\theta' \colon \multiplicativegroup{\finiteFieldExtension{2}} \to \multiplicativegroup{\ladicnumbers}$ be the character given bv $$\theta'\left(x\right) = \theta\left(x^{1-q}\right).$$
	We claim that the torus character pairs $\left(\algebraicGroup{T}_2 \times \algebraicGroup{T}_2, \theta \times \theta\right)$ and $\left(\algebraicGroup{T}'_2, \theta'\right)$ are geometrically conjugate. Indeed, if $m \ge 2$ is even, then $\left(\algebraicGroup{T}'_2\right)^{\Frobenius^{m}} = \multiplicativegroup{\finiteFieldExtension{m}} \times \multiplicativegroup{\finiteFieldExtension{m}}$ and $\algebraicGroup{T}_2^{\Frobenius^m} = \multiplicativegroup{\finiteFieldExtension{m}}$. The norm map $\left(\algebraicGroup{T}'_2\right)^{\Frobenius^{m}} \to \left(\algebraicGroup{T}'_2\right)^{\Frobenius}$ is given by $\multiplicativegroup{\finiteFieldExtension{m}} \times \multiplicativegroup{\finiteFieldExtension{m}} \ni \left(x,y\right) \mapsto \FieldNorm{m}{2}\left(x\right) \FieldNorm{m}{2}\left(y\right)$, while the norm map $\algebraicGroup{T}_2^{\Frobenius^{m}} \to \algebraicGroup{T}_2^{\Frobenius}$ is given by $\multiplicativegroup{\finiteFieldExtension{m}} \ni x \mapsto \FieldNorm{m}{2}\left(x\right)^{1-q}$. We thus have
	$$\left(\theta \times \theta\right) \circ \aFieldNorm_{ \left(\algebraicGroup{T}_2 \times \algebraicGroup{T}_2\right)^{\Frobenius^m} : \left(\algebraicGroup{T}_2 \times \algebraicGroup{T}_2\right)^{\Frobenius} } = \theta' \circ \aFieldNorm_{\left(\algebraicGroup{T}'_2\right)^{\Frobenius^m} \colon \left(\algebraicGroup{T}'_2\right)^{\Frobenius}}.$$
\end{example}

@@

\begin{center}
\begin{tabular}{ c c c c c c}
 Group & Fixed Torus & Frobenius on $X(T)$ & Frobenius on $W$ &Dual Group & Dual Torus \\ 
 $Sp(2n)$ & $(\multiplicativegroup{\finiteField})^n$ & 1 & 1 &$SO(2n+1)$ & $(\multiplicativegroup{\finiteField})^n$\\  
 $GSp(2n)$ & $(\multiplicativegroup{\finiteField})^{n+1}$ & 1 & 1 &$GSpin(2n+1)$ &  $(\multiplicativegroup{\finiteField})^{n+1}$ \\
 $SO(2n)$ & $(\multiplicativegroup{\finiteField})^{n}$ & 1 & 1 &$SO(2n)$ &  $(\multiplicativegroup{\finiteField})^{n}$ \\
 $GO(2n)$ & $(\multiplicativegroup{\finiteField})^{n+1}$ & 1 & 1 &? &  $(\multiplicativegroup{\finiteField})^{n+1}$ \\
 $SO(2n+1)$ & $(\multiplicativegroup{\finiteField})^{n}$ & 1 & 1 &$Sp(2n)$ &  $(\multiplicativegroup{\finiteField})^{n}$ \\
 $GO(2n+1)$ & $(\multiplicativegroup{\finiteField})^{n+1}$ &1 & 1 &? &  $(\multiplicativegroup{\finiteField})^{n+1}$ \\ 
  $U(n)$ & $(\NormOneGroup{2})^{n}$ & -1 & 1 & $U(n)$ &  $(\NormOneGroup{2})^{n}$ 
\end{tabular}
\end{center}

\calvin{non split form of $SO(even)$, is the dual group itself?. The torus I think is $(\mathbb{F}_2)^{Nm=1} \times (\mathbb{F}^\times)^{dim -1}$. The Frobenius action on the characters is $(-1,1,1,1\hdots 1)$ and on $W$ its trivial}

@@

Suppose $T \cong \prod_{j=1}^r \multiplicativegroup{\finiteFieldExtension{k_j}} \times \prod_{i=1}^s \finiteFieldExtension{2m_i}^1$. We compute $g_{T,\rho}(\theta,\psi,\chi)$ using the the split torus $\algebraicGroup{T}^*$ in $G^*$ including into the split torus $\algebraicGroup{T}'$ in $\GL$ in the non unitary case and in the unitary case we use the tori $\algebraicGroup{T}^*$ whose $\finiteField$ points are $(\NormOneGroup{2})^n \subset G^*(\finiteField)$ includes into the torus $\algebraicGroup{T}'$ in $\GL(2n)$ whose $\finiteField$ points are $(\finiteFieldExtension{2}^\times)^n$. We then define $\tilde{T}$ as the $\finiteField$-rational torus corresponding to the Frobenius stable Weyl group orbit of $\rho(w)$ inside $W(\algebraicGroup{T}')$ where $(w)$ inside $W(\algebraicGroup{T}^*)$ is the Frobenius stable Weyl group orbit associated to $T$. \Cref{lem:cochar_computation} above implies that
\[
g_{T,\rho}(\theta,\psi,\chi)= g_{T}(\theta,\psi,\chi) \cdot \begin{cases}
        1  & G \neq Sp, GSp\\
        \tau(1,\psi_1) & G = Sp \textnormal{ or } GSp
    \end{cases}.
\]
\Cref{cor:geoconj} then implies that $g_T(\theta,\psi,\chi)$ only depends on the geometric conjugacy class of $(T,\theta)$.   
\begin{comment}
We will have to treat the unitary group case seperatedly. First for the non-unitary group case:\\

@@

\begin{theorem}\label{thm:doubling-method-gamma-factor-for-deligne-lusztig}
	Let $T \subset H$ be a maximal torus and let $\theta \colon T \to \multiplicativegroup{\cComplex}$ be a character. Write $$R_{T,\theta} = \sum_{\Pi} c_{\Pi} \trace \Pi,$$
	where $\Pi$ goes over all the irreducible representations of $H$ and $c_{\Pi} \in \zIntegers$. Suppose that $\pi$ is an irreducible representation such that $c_{\pi} \ne 0$. Then $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = g_T\left(\theta, \fieldCharacter\right).$$
\end{theorem}

\calvin{start alternate writeup of section 3.4/3.4.1:}
\subsection{Computation for Lusztig Series}
The goal of this section is to prove \Cref{thm:Phi_stable} in particular:
\begin{theorem}
\label{thm:doubling-method-gamma-factor-for-deligne-lusztig} If $c_{\pi}$ is nonzero in the virtual representation $R_T(\theta) = \sum c_{\pi} \pi$ then
$$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = g_T\left(\theta, \fieldCharacter\right)$$
\end{theorem}
\calvin{add in $\chi$} the right hand side of which we showed in \Cref{lem:indep_geo_conj} only depends on the geometric conjugacy class of $(T,\theta)$ hence on the Lusztig series $\LusztigSeries{G}{s}$ which contains $\pi$.
\subsubsection{Proof of \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig}, \Cref{thm:Phi_stable}}
Our proof will be via induction on $\dim_{\quadraticExtension} \hermitianSpace$. First we will use \Cref{thm:multiplicativity-in-terms-of-gamma-factors}  and MULTIPLICAATIVITY-OF-GTTHETA to prove \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for any non cuspidal $\pi$ assuming \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for all Levi factors. \\

@@

\calvin{end alternate writeup}
\calvin{start alternate writeup 2 of section 3.4/3.4.1}
\subsection{Computation for Lusztig Series}
The goal of this section is to prove \Cref{thm:Phi_stable} in particular:
\begin{theorem}
\label{thm:doubling-method-gamma-factor-for-deligne-lusztig} If $c_{\pi}$ is nonzero in the virtual representation $R_T(\theta) = \sum c_{\pi} \pi$ then
$$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = g_T\left(\theta, \fieldCharacter\right)$$
\end{theorem}
\calvin{add in $\chi$} the right hand side of which we showed in \Cref{lem:indep_geo_conj} only depends on the geometric conjugacy class of $(T,\theta)$ hence on the Lusztig series $\LusztigSeries{G}{s}$ which contains $\pi$.
\subsubsection{Proof of \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig}, \Cref{thm:Phi_stable}}
We instead prove a version of \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for the extension $\GroupExtension{G}$ (see section 3.2) of $G$:
\begin{theorem}
\label{thm:doubling-method-gamma-factor-for-deligne-lusztig-extensions} Extend $\Phi_{\chi}$ by zero to $\GroupExtension{G}$. If $c_{\pi}$ is nonzero in the virtual representation $R_{T}(\theta) = \sum c_{\pi} \pi$ of $\GroupExtension{G}$ then
$$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = g_{T \cap G}\left(\theta|_{T \cap G}, \fieldCharacter\right)$$
where the doubling factor is defined by
\[
\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} := \omega_{\pi}(-1)\frac{\sum_{g \in \GroupExtension{G}}\pi(g)\Phi_{\chi}(g)}{\sqrt{|g|}c_V(\chi,\pi)}
\]
\elad{Note that on page 6 we already defined $\dblJacobiSum{\pi}{\chi}$ by only summing on the $G$ points. Same for $\dblJacobiSumScalar{F}{\chi}$ on page 9.}
\end{theorem}
Any irreducible representation $\pi$ of $G$ which is the a component of an irreducible representation $\tilde{\pi}$ of $\GroupExtension{G}$ restricted to $\pi$,
\[
    \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \dblGammaFactorSpace{\hermitianSpace}{\tilde{\pi}}{\chi}{\fieldCharacter}.
\]

The following proposition implies that if $\pi \in \LusztigSeries{\FrobeniusFixedPoints{G}}{s}$ then there exists $\tilde{\pi} \in \LusztigSeries{\FrobeniusFixedPoints{G}}{\tilde{s}}$ for $\tilde{s}$ only dependeing on $s$. Thus \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} follows from \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig-extensions}.

@@

Our proof will be via induction on $\dim_{\quadraticExtension} \hermitianSpace$. First we will use \Cref{thm:multiplicativity-in-terms-of-gamma-factors}  and MULTIPLICAATIVITY-OF-GTTHETA to prove \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig-extensions} for any non cuspidal $\pi$ assuming \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig-extensions} for all Levi factors. \\

@@

But it is well known that there is only one cuspidal $\pi$:
\begin{proposition}[{\cite[Page 172]{Lusztig1977}}]
	Let $\GroupExtension{G}$ have connected center. For any semisimple element $s \in \DualFrobeniusFixedPoints{\GroupExtension{G}}$, the Lusztig series $\LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{s}$ contains at most one cuspidal element.
\end{proposition}

So the proof of \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig-extensions} is complete.

>>>>

	\item (Special even orthogonal groups): $\quadraticExtension = \finiteField$ and $\epsilon_{\hermitianSpace} = 1$. Denote $\dim_{\finiteField} \hermitianSpace = 2n$. It follows by definition that every element $g \in \IsometryGroup\left(\hermitianSpace\right)$ satisfies $\left(\det g\right)^2 = 1$. Similarly, every element $g \in \widetilde{\IsometryGroup\left(\hermitianSpace\right)}$ satisfies $\left(\det g\right)^2 = \similitudeCharacter\left(g\right)^{2n}$. In this case, we obtain the connected components of the identity by adding a restriction on the determinant: We have that $G$ consists of all elements $g \in \IsometryGroup\left(\hermitianSpace\right)$ with $\det g = 1$, and that $\GroupExtension{G}$ consists of all elements $g \in \GroupExtension{\IsometryGroup\left(\hermitianSpace\right)}$ such that $\det g = \similitudeCharacter\left(g\right)^n$. There are two cases here.

@@

\begin{example}
	Take $\algebraicGroup{G}' = \algebraicGroup{\GL}_2$. Let $\algebraicGroup{T}'_2 = \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme}$ and $$\algebraicGroup{T}_2 = \left\{x \in \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme} \mid x \involution{x} = 1 \right\}.$$
	Then $\left(\algebraicGroup{T}'_2\right)^{\Frobenius} = \multiplicativegroup{\finiteFieldExtension{2}}$ and $\algebraicGroup{T}_2^{\Frobenius} = \NormOneGroup{2}$. Let $\theta \colon \NormOneGroup{2} \to \multiplicativegroup{\ladicnumbers}$ be a character, and let $\theta' \colon \multiplicativegroup{\finiteFieldExtension{2}} \to \multiplicativegroup{\ladicnumbers}$ be the character given bv $$\theta'\left(x\right) = \theta\left(x^{1-q}\right).$$
	We claim that the torus character pairs $\left(\algebraicGroup{T}_2 \times \algebraicGroup{T}_2, \theta \times \theta\right)$ and $\left(\algebraicGroup{T}'_2, \theta'\right)$ are geometrically conjugate. Indeed, if $m \ge 2$ is even, then $\left(\algebraicGroup{T}'_2\right)^{\Frobenius^{m}} = \multiplicativegroup{\finiteFieldExtension{m}} \times \multiplicativegroup{\finiteFieldExtension{m}}$ and $\algebraicGroup{T}_2^{\Frobenius^m} = \multiplicativegroup{\finiteFieldExtension{m}}$. The norm map $\left(\algebraicGroup{T}'_2\right)^{\Frobenius^{m}} \to \left(\algebraicGroup{T}'_2\right)^{\Frobenius}$ is given by $\multiplicativegroup{\finiteFieldExtension{m}} \times \multiplicativegroup{\finiteFieldExtension{m}} \ni \left(x,y\right) \mapsto \FieldNorm{m}{2}\left(x\right) \FieldNorm{m}{2}\left(y\right)$, while the norm map $\algebraicGroup{T}_2^{\Frobenius^{m}} \to \algebraicGroup{T}_2^{\Frobenius}$ is given by $\multiplicativegroup{\finiteFieldExtension{m}} \ni x \mapsto \FieldNorm{m}{2}\left(x\right)^{1-q}$. We thus have
	$$\left(\theta \times \theta\right) \circ \aFieldNorm_{ \left(\algebraicGroup{T}_2 \times \algebraicGroup{T}_2\right)^{\Frobenius^m} : \left(\algebraicGroup{T}_2 \times \algebraicGroup{T}_2\right)^{\Frobenius} } = \theta' \circ \aFieldNorm_{\left(\algebraicGroup{T}'_2\right)^{\Frobenius^m} \colon \left(\algebraicGroup{T}'_2\right)^{\Frobenius}}.$$
\end{example}

@@

\begin{center}
	\begin{tabular}{ c c c c c c}
		$\algebraicGroup{G}$ & $\algebraicGroup{T} \subset \algebraicGroup{G}$ & $\Frobenius$ action on $\CharacterLattice{\algebraicGroup{T}}$ & $\algebraicGroup{G}^{\ast}$ & $\algebraicGroup{T}^{\ast} \subset \algebraicGroup{G}^{\ast}$  \\
		$\algebraicGroup{\UnitaryGroup}_n$ & $(\algebraicGroup{\UnitaryGroup}_1)^{n}$ & $\left(-1\right)^{\times n}$ & $\algebraicGroup{\UnitaryGroup}_n$ &  $(\algebraicGroup{\UnitaryGroup}_1)^{n}$ \\		 
		$\algebraicGroup{\SO}_{2n+1}$ & $\multiplcativeScheme^n$ & 1 &$\algebraicGroup{\Sp_{2n}}$ &  $\multiplcativeScheme^n$ \\	
		$\algebraicGroup{\Sp}_{2n}$ & $\multiplcativeScheme^n$ & 1 &$\algebraicGroup{\SO}_{2n+1}$ & $\multiplcativeScheme^n$\\  			 
		$\algebraicGroup{\SO}^{+}_{2n}$ & $\multiplcativeScheme^n$ & 1 &$\algebraicGroup{\SO}^{+}_{2n}$ &  $\multiplcativeScheme^n$ \\
		$\algebraicGroup{\SO}^{-}_{2n}$ & $\multiplcativeScheme^{n-1} \times \algebraicGroup{\UnitaryGroup}_1$ & $\left(1\right)^{\times {\left(n-1\right)}} \times \left(-1\right)$ &$\algebraicGroup{\SO}^{-}_{2n}$ &  $\multiplcativeScheme^{n-1} \times \algebraicGroup{\UnitaryGroup}_1$ \\
		 $\algebraicGroup{\GSp}_{2n}$ & $\multiplcativeScheme \times \multiplcativeScheme^{n}$ & 1 &$\algebraicGroup{GSpin}_{2n+1}$ &  $\multiplcativeScheme \times \multiplcativeScheme^{n}$ \\
		 $\algebraicGroup{\GSO}^{+}_{2n}$ & $\multiplcativeScheme \times \multiplcativeScheme^{n}$ & 1 & $\algebraicGroup{GSpin}_{2n}^{+}$ &  $\multiplcativeScheme \times \multiplcativeScheme^{n}$ \\
		 $\algebraicGroup{\GSO}^{-}_{2n}$ & $\multiplcativeScheme^{n-1} \times \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme}$ & $\left(1\right)^{\times {\left(n-1\right)}} \times \sigma^{\ast}$ & $\algebraicGroup{GSpin}_{2n}^{-}$ &  $\multiplcativeScheme^{n-1} \times \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme}$		 
\end{tabular}
\end{center}
For all the pairs $\algebraicGroup{T} \subset \algebraicGroup{G}$ in this list, the Frobenius root $\Frobenius$ of $\algebraicGroup{G}$ acts trivially on the Weyl group $W\left(\algebraicGroup{T}\right)$. In the last row, $\sigma \colon \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme} \to \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme}$ is the automorphism $a + b\sqrt{d} \mapsto a - b\sqrt{d}$ where $d \in \multiplicativegroup{\finiteField}$ is a non-square.

@@

Suppose $T \cong \prod_{j=1}^r \multiplicativegroup{\finiteFieldExtension{k_j}} \times \prod_{i=1}^s \finiteFieldExtension{2m_i}^1$. We compute $g_{T,\rho}(\theta,\psi,\chi)$ using the the split torus $\algebraicGroup{T}^*$ in $G^*$ including into the split torus $\algebraicGroup{T}'$ in $\GL$ in the non unitary case and in the unitary case we use the tori $\algebraicGroup{T}^*$ whose $\finiteField$ points are $(\NormOneGroup{2})^n \subset G^*(\finiteField)$ includes into the torus $\algebraicGroup{T}'$ in $\GL(2n)$ whose $\finiteField$ points are $(\finiteFieldExtension{2}^\times)^n$. We then define $\tilde{T}$ as the $\finiteField$-rational torus corresponding to the Frobenius stable Weyl group orbit of $\rho(w)$ inside $W(\algebraicGroup{T}')$ where $(w)$ inside $W(\algebraicGroup{T}^*)$ is the Frobenius stable Weyl group orbit associated to $T$. \Cref{lem:cochar_computation} above implies that
\[
g_{T,\rho}(\theta,\psi,\chi)= g_{T}(\theta,\psi,\chi) \cdot \begin{cases}
        1  & G \neq Sp, GSp\\
        \tau(1,\psi_1) & G = Sp \textnormal{ or } GSp
    \end{cases}.
\]
\calvin{check if we need a $\chi$ in the $\tau$ factor}
\Cref{cor:geoconj} then implies that $g_T(\theta,\psi,\chi)$ only depends on the geometric conjugacy class of $(T,\theta)$.   
\begin{comment}
We will have to treat the unitary group case seperatedly. First for the non-unitary group case:\\

@@

\begin{theorem}\label{thm:doubling-method-gamma-factor-for-deligne-lusztig}
	Let $T \subset H$ be a maximal torus and let $\theta \colon T \to \multiplicativegroup{\cComplex}$ be a character. Write $$R_{T,\theta} = \sum_{\Pi} c_{\Pi} \trace \Pi,$$
	where $\Pi$ goes over all the irreducible representations of $H$ and $c_{\Pi} \in \zIntegers$. Suppose that $\pi$ is an irreducible representation such that $c_{\pi} \ne 0$. Then $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = g_T\left(\theta, \fieldCharacter\right).$$
\end{theorem}
\begin{comment}
\calvin{start alternate writeup of section 3.4/3.4.1:}
\subsection{Computation for Lusztig Series}
The goal of this section is to prove \Cref{thm:Phi_stable} in particular:
\begin{theorem}
\label{thm:doubling-method-gamma-factor-for-deligne-lusztig} If $c_{\pi}$ is nonzero in the virtual representation $R_T(\theta) = \sum c_{\pi} \pi$ then
$$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = g_T\left(\theta, \fieldCharacter\right)$$
\end{theorem}
\calvin{add in $\chi$} the right hand side of which we showed in \Cref{lem:indep_geo_conj} only depends on the geometric conjugacy class of $(T,\theta)$ hence on the Lusztig series $\LusztigSeries{G}{s}$ which contains $\pi$.
\subsubsection{Proof of \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig}, \Cref{thm:Phi_stable}}
Our proof will be via induction on $\dim_{\quadraticExtension} \hermitianSpace$. First we will use \Cref{thm:multiplicativity-in-terms-of-gamma-factors}  and MULTIPLICAATIVITY-OF-GTTHETA to prove \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for any non cuspidal $\pi$ assuming \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for all Levi factors. \\

@@

\calvin{end alternate writeup}
\end{comment}
\calvin{start alternate writeup 2 of section 3.4/3.4.1}
\subsection{Computation for Lusztig Series}
The goal of this section is to prove \Cref{thm:Phi_stable} in particular:
\begin{theorem}
\label{thm:doubling-method-gamma-factor-for-deligne-lusztig} For either $G=G$ or its group extension $\GroupExtension{G}$. If $c_{\pi}$ is nonzero in the virtual representation $R_T(\theta) = \sum c_{\pi} \pi$ then
$$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = g_{T \cap G}\left(\theta|_{T \cap G}, \fieldCharacter\right)$$
\end{theorem}
\calvin{add in $\chi$} the right hand side of which we showed in \Cref{lem:indep_geo_conj} only depends on the geometric conjugacy class of $(T,\theta)$ hence on the Lusztig series $\LusztigSeries{G}{s}$ which contains $\pi$.
\subsubsection{Proof of \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig}, \Cref{thm:Phi_stable}}
We first reduce \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} to the case $G$ has connected center. For any irreducible representation $\pi$ of $G$ which is the a component of an irreducible representation $\tilde{\pi}$ of $\GroupExtension{G}$ restricted to $\pi$,
\[
    \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \dblGammaFactorSpace{\hermitianSpace}{\tilde{\pi}}{\chi}{\fieldCharacter}.
\]

The following proposition implies that if $\pi \in \LusztigSeries{\FrobeniusFixedPoints{G}}{s}$ then there exists $\tilde{\pi} \in \LusztigSeries{\FrobeniusFixedPoints{G}}{\tilde{s}}$ for $\tilde{s}$ only depending on $s$. Thus \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for $G$ follows from \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for $\GroupExtension{G}$ (see section 3.2).

@@

We now prove \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for the extension $\GroupExtension{G}$.

Our proof will be via induction on $\dim_{\quadraticExtension} \hermitianSpace$. First we will use \Cref{thm:multiplicativity-in-terms-of-gamma-factors}  and MULTIPLICAATIVITY-OF-GTTHETA to prove \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for any non cuspidal $\pi$ assuming \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for all Levi factors. \\

@@

But it is well known that there is only one cuspidal $\pi$ appearing in our sum:
\begin{proposition}[{\cite[Page 172]{Lusztig1977}}]
	Let $\GroupExtension{G}$ have connected center. For any semisimple element $s \in \DualFrobeniusFixedPoints{\GroupExtension{G}}$, the Lusztig series $\LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{s}$ contains at most one cuspidal element.
\end{proposition}

So the proof of \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} is complete.
